Report and Figures

### 2016-11-12 figs.Rmd
resized figs

out_dir <- paste0('figs/prominence_map_Detroit.pdf')
ggsave(out_dir, width = 14, height = 14, units = 'cm')
embed_fonts(out_dir, outfile=out_dir)

@@

  }else{
    guide = FALSE
  }

@@

@@

  out_dir <- paste0('figs/cluster_map_', city, '.pdf')
  ggsave(out_dir, width = 14, height = 10, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)
}
```

>>>>

out_dir <- paste0('figs/prominence_map_Detroit.pdf')
ggsave(out_dir, width = 14, height = 10, units = 'cm')
embed_fonts(out_dir, outfile=out_dir)

@@

  }else{
    guide = FALSE
  }
  if(city == 'Detroit'){
    height = 10
  }else{
    height = 14
  }

@@

  ggsave(out_dir, width = 14, height = height, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)

@@

  out_dir <- paste0('figs/cluster_map_', city, '.pdf')
  ggsave(out_dir, width = 14, height = height, units = 'cm')
  embed_fonts(out_dir, outfile=out_dir)
}
```
